How to Find GENERAL Defect Prediction Models \\ Amidst Hundreds of Software Projects

### 2020-03-03 response.tex

\review{(1.8) As mentioned in one of my comments above, the script seeks to model generalizability looking at the number of projects (and size) as solely dimension to look at. But what about the quality attributes, such as the application domain? What are the application domains of the projects? Are there only open-source projects? How about industrial projects, including the financial, automotive, and robotics sectors? How many web and mobile applications are in the sample? Does the dataset cover these domains? If not, how can we claim that 700 projects can bring us to generalizability?}

not in general. cant prove external validity. jsut for our 673 projects. wichi is orders of mangitude larger than anything seen ebfore.

\review{(1.9) Furthermore, the dataset looks quite strange to me. Looking at the defect distributions (left-most boxplot in Figure 4), I do see that 75\% of the projects (the last quartile) have more than 60\% of defective modules (classes/methods?). Some have a defective percentage above 80\%. Do we need machine learning to predict defects in projects where almost all modules are defectives? In these projects, a simple, constant classifier would work the best. The results also show this for ZeroR in Section 5.}

unclear on this. zeroR tells us that it is not enough to do simple things

\review{(3.10) Throughout the manuscript, the complexity of GENERAL is suggested to be $O(m * (N/m)^2)$. But there is proof about the complexity whatsoever. Either the manuscript cites proofs from existing papers (e.g., related work on hierarchical clustering) or provides a complete proof (perhaps in an appendix).}

XXXX

\review{(1.11) All the results are summarized in one single table (Figure 7), which shows the mean and the standard deviation of five evaluation metrics, as well as the rank of the statistical tests. There are two problems in aggregating the data in this way: (1)I am not sure that the arithmetic mean and the standard deviation are the appropriate metrics to use. Are the data normally distributed? Do we have many outliers? Perhaps, median and IQR are more appropriate as they are less affected by outliers.}

use medians an QRQ

{Maybe, the boxplots would be the most appropriate way to show the distributions. (2)The average across 700 projects makes little sense and hides what happens in each project. What happens per project? In how many projects does GENERAL performs better than the standard bellwether learner?}

xplain

\review{(1.12) Section 5 contains the following recommendation “As to ZeroR, we cannot recommend that approach. While ZeroR makes few mistakes (low ifas and low pfs), it scores badly on other measures (very low recalls and popt(20).” This argument does not convince me as ZeroR gets the best results for two metrics (as far as I understand). Please elaborate more on why we cannot use ZeroR. Besides, ZeroR may work relatively well because of projects with a very large number of defects. Perhaps, some in-depth analysis of the correlation between defect distributions and performances of the models would be very useful.}

Xplan

\review{(1.13) Section 5 (RQ3) ends with two recommendations about critical and non-critical systems. However, I could not find any analysis that can support these recommendations. I also queried the paper looking for the keywords “critical systems,” but I could not find anything except the recommendation with these keywords. To address this, there are only two mutually exclusive solutions: either remove the recommendations or add in-depth analysis that can provide empirical evidence to the claims.}

cget rid of critial systems
